Cleaning Tropical Andes frugivore GBIF occurrence records

### 2024-06-10 code/L1/L1_F1_TropicalAndes_frugivores_GBIF.Rmd
update to use data_summary function

```{r}
print("The number of records is")
nrow(TropicalAndes_GBIF_frugivore_occ_cleaned)
print("The number of species is")
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$species))
print("The number of genera is" )
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$genus))
print("The number of families is")
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$family))
```

>>>>

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")

data_summary(TropicalAndes_GBIF_frugivore_occ_cleaned, TropicalAndes_GBIF_frugivore_occ_cleaned$species, TropicalAndes_GBIF_frugivore_occ_cleaned$genus, TropicalAndes_GBIF_frugivore_occ_cleaned$family)
```
